---
title: "IU length for various words"
author: "Lu Liu, Haoran Yan & Ryan Ka Yau Lai"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, echo=FALSE}
library(knitr)
# set global chunk options: images will be 7x5 inches
knitr::opts_chunk$set(fig.width=7, fig.height=5)
options(digits = 4)
```

```{r, include=FALSE}
# for debugging latex
options(tinytex.verbose = TRUE)
```

```{r}
library(tidyverse)
library(rstan)
library(tidyr)
library(HMMpa)
```

## Getting started

```{r}
load("/Users/lu/Desktop/Winter_2023/sb corpus/sbc.Rdata")
#load("G:\\共用雲端硬碟\\Prosody & Units in Dialogue\\Staircases\\reorganised_code\\sbc.Rdata")
```

Get SBC data ready:
```{r}
sbc <- sbc %>%
  group_by(docId, unitId) %>%
  mutate(unitLenWords = suppressWarnings(max(place, na.rm = T))) %>%
  ungroup
```

## Implementing the model

Function for getting the NegBin / Poisson models:
```{r}
getModel = function(word, back = F){
  data_raw <- sbc %>%
    filter(tolower(text) == word) %>%
    filter(!is.na(place))
  
  if(!back){
    data_input <- list(
      N = nrow(data_raw),
      place = pull(data_raw, place),
      unit_length = pull(data_raw, unitWordLen)
    )
  } else {
    data_input <- list(
      N = nrow(data_raw),
      place = pull(data_raw, unitWordLen) - pull(data_raw, place) + 1,
      unit_length = pull(data_raw, unitWordLen)
    )
  }

  stan(
    file = "He_place_given_length_NB.stan",
    data = data_input,
    chain = 4,
    cores = getOption("mc.cores", 4)
  )
}
```

Implementing the models:
```{r}
#the, little, an, just, would, he
model_negbin_pois_the = getModel("the", back = T)
model_negbin_pois_right = getModel("right", back = T)
model_negbin_pois_little = getModel("little", back = T)
model_negbin_pois_an = getModel("an", back = T)
model_negbin_pois_just = getModel("just")
model_negbin_pois_would = getModel("would")
model_negbin_pois_he = getModel("he")
model_negbin_pois_yes = getModel("yes")
```

```{r}
getVar = function(model){
  extracted = extract(model)
  mean(extracted$mu * (1 + extracted$mu / extracted$phi))
}
getVar(model_negbin_pois_the)
getVar(model_negbin_pois_right)
getVar(model_negbin_pois_little)
getVar(model_negbin_pois_an)
getVar(model_negbin_pois_just)
getVar(model_negbin_pois_would) 
getVar(model_negbin_pois_he)
getVar(model_negbin_pois_yes)

```









```{r}

sbc$place_minus_1 = sbc$place - 1

sbc$length_minus_1 = sbc$unitWordLen - 1

```


```{r}
getModel = function(word, file_path, back = F){
  data_raw <- sbc %>%
    filter(tolower(text) == word) %>%
    filter(!is.na(place))
  
  if(!back){
    data_input <- list(
      N = nrow(data_raw),
      place = pull(data_raw, place_minus_1),
      unit_length = pull(data_raw, length_minus_1)
    )
  } else {
    data_input <- list(
      N = nrow(data_raw),
      place = pull(data_raw, unitWordLen) - pull(data_raw, place) + 1,
      unit_length = pull(data_raw, unitWordLen)
    )
  }

  stan(
    file = file_path,
    data = data_input,
    chain = 4,
    cores = getOption("mc.cores", 4)
  )
}

```
## Normal Poisson

### he

```{r}
pois_he = getModel("he", "Stan/He_place_given_length_NB.stan", back = F)
```


```{r}
he <- sbc %>%
  filter(tolower(text) == 'he') %>%
  filter(!is.na(place))

```

#### generate quantities
```{r}
nb_lambda_he <- extract(pois_he, pars = c("lambda"))
nb_phi_he <- extract(pois_he, pars = c("phi"))
nb_mu_he <- extract(pois_he, pars = c("mu"))

he_final = data.frame()
# iterate through 4000 times
for (i in 1:1000) {
  
  
  # generate length
  nb_length <- rnbinom(length(he$length_minus_1), size = nb_phi_he$phi[i], 
                         prob = nb_phi_he$phi[i] / (nb_phi_he$phi[i] + nb_mu_he$mu[i]))
  
  nb_place <- c()
  for (length_val in nb_length) {
    nb_place <- c(nb_place, rpois(1, nb_lambda_he$lambda[i]))

  }
  he_generated <- data.frame(nb_length, nb_place)
  he_final <- rbind(he_final, he_generated)
}

```

#### Visualization

```{r}

all_df <- data.frame(nb_length = numeric(), nb_place = numeric(), n.x = numeric(), n.y = numeric())
num_iterations <- nrow(he_final) / length(he$unitWordLen)

for (i in 1:num_iterations) {
  start_index <- (i - 1) * length(he$unitWordLen) + 1
  end_index <- i * length(he$unitWordLen)
  
  subset_data <- he_final[start_index:end_index, ] %>% group_by(nb_length, nb_place) %>% count
  
  subset <- subset_data[subset_data$nb_length < 15 & subset_data$nb_length >= 1,]
  result <- aggregate(n ~ nb_length, data = subset, FUN = sum)
  
  merged_df <- merge(subset, result, by = "nb_length")
  
  all_df <- rbind(all_df, merged_df)
}

group <- he[c("unitWordLen", "place")]
colnames(group) <- c("nb_length", "nb_place")

group <- group %>% group_by(nb_length, nb_place) %>% count
subset <- group[group$nb_length < 15 & group$nb_length > 1,]
result <- aggregate(n ~ nb_length, data = subset, FUN = sum)
result <- merge(subset, result, by = "nb_length")


```


```{r fig.height=400, fig.width=500}

p <- ggplot(data = all_df, aes(x = nb_place, y = n.x/n.y)) +
    geom_point(alpha = .015, position = "jitter")
    
p <- p + facet_wrap("nb_length") + geom_point(data = result %>% filter(nb_length <= 14), color = "red") + facet_wrap("nb_length")

```


###########################################################################################

## Get model with minus 1

```{r}
getModel = function(word, file_path, back = F){
  data_raw <- sbc %>%
    filter(tolower(text) == word) %>%
    filter(!is.na(place))
  
  if(!back){
    data_input <- list(
      N = nrow(data_raw),
      place = pull(data_raw, place_minus_1),
      unit_length = pull(data_raw, length_minus_1)
    )
  } else {
    data_input <- list(
      N = nrow(data_raw),
      place = pull(data_raw, length_minus_1) - pull(data_raw, place_minus_1) + 1,
      unit_length = pull(data_raw, length_minus_1)
    )
  }

  stan(
    file = file_path,
    data = data_input,
    chain = 4,
    cores = getOption("mc.cores", 4)
  )
}

```

## Generalized Poisson

### he

```{r}
gen_pois_he = getModel("he", "Stan/gen_pois.stan", back = F)

```

```{r}
gen_pois_he
```


```{r}
he <- sbc %>%
  filter(tolower(text) == 'he') %>%
  filter(!is.na(place))

```

#### generate quantities

```{r}
set.seed(123)
theta = 0.7823
lambda = 0.3263
unit_length = 9


trun_rgen <- function(theta, lambda, unit_length, word, max_length) {
  prob_list <- c()
  y_list <- c()
  for (y in 0:max_length) {
    prob <- (theta * (theta + lambda * y)^(y-1)) * exp(-theta - lambda * y) / factorial(y)
    prob_list <- c(prob_list, prob)
    y_list <- c(y_list, y)
  }
  
  cdf <- data.frame(Value = y_list, Proportion = prob_list)
  cdf$cum_sum = cumsum(cdf$Proportion)
  
  F_L <- cdf[cdf$Value == unit_length, ]$cum_sum
  cdf$trun_sum <- cdf$cum_sum
  cdf$trun_sum[cdf$Value <= unit_length] <- cdf$cum_sum[cdf$Value <= unit_length] / F_L

  cdf$trun_sum[cdf$Value > unit_length] <- 1
  
  cdf$trun_pmf <- c(cdf$trun_sum[1], diff(cdf$trun_sum))
  
  quantities <- sample(cdf$Value, size = 1, replace = TRUE, prob = cdf$trun_pmf)
  return(quantities)
}

```

```{r}
set.seed(123)
nb_theta_he <- extract(gen_pois_he, pars = c("theta1"))
nb_lambda_he <- extract(gen_pois_he, pars = c("lambda1"))
nb_phi_he <- extract(gen_pois_he, pars = c("phi"))
nb_mu_he <- extract(gen_pois_he, pars = c("mu"))

he_final = data.frame()
# iterate through 4000 times
for (i in 1:200) {
  
  
  # generate length
  nb_length <- rnbinom(length(he$length_minus_1), size = nb_phi_he$phi[i], 
                         prob = nb_phi_he$phi[i] / (nb_phi_he$phi[i] + nb_mu_he$mu[i]))
  
  nb_place <- c()
  max_length <- max(nb_length)
  for (length_val in nb_length) {
    nb_place <- c(nb_place, trun_rgen(nb_theta_he$theta1[i], nb_lambda_he$lambda1[i], length_val, he, max_length))

  }
  he_generated <- data.frame(nb_length, nb_place)
  he_final <- rbind(he_final, he_generated)
}

```

#### Visualization

```{r}

all_df <- data.frame(nb_length = numeric(), nb_place = numeric(), n.x = numeric(), n.y = numeric())
num_iterations <- nrow(he_final) / length(he$length_minus_1)

for (i in 1:num_iterations) {
  start_index <- (i - 1) * length(he$length_minus_1) + 1
  end_index <- i * length(he$length_minus_1)
  
  subset_data <- he_final[start_index:end_index, ] %>% group_by(nb_length, nb_place) %>% count
  
  subset <- subset_data[subset_data$nb_length < 15,]
  result <- aggregate(n ~ nb_length, data = subset, FUN = sum)
  
  merged_df <- merge(subset, result, by = "nb_length")
  
  all_df <- rbind(all_df, merged_df)
}

group <- he[c("length_minus_1", "place_minus_1")]
colnames(group) <- c("nb_length", "nb_place")

group <- group %>% group_by(nb_length, nb_place) %>% count
subset <- group[group$nb_length < 15,]
result <- aggregate(n ~ nb_length, data = subset, FUN = sum)
result <- merge(subset, result, by = "nb_length")

```



```{r fig.height=400, fig.width=500}

p <- ggplot(data = all_df, aes(x = nb_place, y = n.x/n.y)) +
    geom_point(alpha = .015, position = "jitter")
    
p <- p + facet_wrap("nb_length") + geom_point(data = result %>% filter(nb_length <= 14), color = "red") + facet_wrap("nb_length")

```

## Hurdle model 

### he

```{r}
gen_pois_he_hurdle = getModel("he", "Stan/gen_pois_hurdle.stan", back = T)
```

#### Generating quantities

```{r}
# write a function for cdf
# draw from uniform distribution, the value of x such

# Use the parameters, get cdf of generalized poisson, draw random number from 0 to 1

nb_theta_he <- extract(gen_pois_he_hurdle, pars = c("theta1"))
nb_lambda_he <- extract(gen_pois_he_hurdle, pars = c("lambda1"))
nb_phi_he <- extract(gen_pois_he_hurdle, pars = c("phi"))
nb_mu_he <- extract(gen_pois_he_hurdle, pars = c("mu"))
nb_psi_he <- extract(gen_pois_he_hurdle, pars = c("psi"))

he_final = data.frame()
# iterate through 4000 times
for (i in 1:4000) {
  
  
  # generate length
  nb_length <- rnbinom(length(he$length_minus_1), size = nb_phi_he$phi[i], 
                         prob = nb_phi_he$phi[i] / (nb_phi_he$phi[i] + nb_mu_he$mu[i]))
  
  nb_place <- c()
  max_length <- max(nb_length)
  for (length_val in nb_length) {
    nb_place <- c(nb_place, trun_hurdle(nb_psi_he$psi[i], nb_theta_he$theta1[i], 
                                        nb_lambda_he$lambda1[i], length_val, he, max_length))

  }
  he_generated <- data.frame(nb_length, nb_place)
  he_final <- rbind(he_final, he_generated)
}

```


#### visualization

```{r}

all_df <- data.frame(nb_length = numeric(), nb_place = numeric(), n.x = numeric(), n.y = numeric())
num_iterations <- nrow(s_final) / length(s$length_minus_1)

for (i in 1:num_iterations) {
  start_index <- (i - 1) * length(s$length_minus_1) + 1
  end_index <- i * length(s$length_minus_1)
  
  subset_data <- s_final[start_index:end_index, ] %>% group_by(nb_length, nb_place) %>% count
  
  subset <- subset_data[subset_data$nb_length < 15,]
  result <- aggregate(n ~ nb_length, data = subset, FUN = sum)
  
  merged_df <- merge(subset, result, by = "nb_length")
  
  all_df <- rbind(all_df, merged_df)
}

group <- s[c("length_minus_1", "place_minus_1")]
colnames(group) <- c("nb_length", "nb_place")

group <- group %>% group_by(nb_length, nb_place) %>% count
subset <- group[group$nb_length < 15,]
result <- aggregate(n ~ nb_length, data = subset, FUN = sum)
result <- merge(subset, result, by = "nb_length")

```

```{r fig.height=400, fig.width=500}

p <- ggplot(data = all_df, aes(x = nb_place, y = n.x/n.y)) +
    geom_point(alpha = .015, position = "jitter")
    
p <- p + facet_wrap("nb_length") + geom_point(data = result %>% filter(nb_length <= 14), color = "red") + facet_wrap("nb_length")

```


### 's


```{r}

gen_pois_s_hurdle = getModel("'s", "Stan/gen_pois_hurdle.stan", back = F)

s <- sbc %>%
  filter(tolower(text) == "'s") %>%
  filter(!is.na(place))
```

#### generate quantities

```{r}
set.seed(123)
theta = 4.002e-01
lambda = 3.812e-01
unit_length = 9
psi1 = 5.600e-04
psi2 = 6.600e-04

trun_hurdle <- function(psi1, psi2, theta, lambda, unit_length, word, max_length) {
  prob_list <- c()
  y_list <- c()
  prob_list <- c(prob_list, psi1, psi2)
  y_list <- c(y_list, 0, 1)
  
  for (y in 2:max_length) {
    prob <- (1-psi1-psi2)* ((theta * (theta + lambda * y)^(y-1)) * exp(-theta - lambda * y) / factorial(y))/ 
      (1 - (theta * theta^(-1) * exp(-theta)) - (theta * exp(-theta - lambda)) / 2)



    prob_list <- c(prob_list, prob)
    y_list <- c(y_list, y)
  }
  
  cdf <- data.frame(Value = y_list, Proportion = prob_list)
  cdf$cum_sum = cumsum(cdf$Proportion)
  
  F_L <- cdf[cdf$Value == unit_length, ]$cum_sum
  cdf$trun_sum <- cdf$cum_sum
  cdf$trun_sum[cdf$Value <= unit_length] <- cdf$cum_sum[cdf$Value <= unit_length] / F_L

  cdf$trun_sum[cdf$Value > unit_length] <- 1
  
  cdf$trun_pmf <- c(cdf$trun_sum[1], diff(cdf$trun_sum))
  
  quantities <- sample(cdf$Value, size = 1, replace = TRUE, prob = cdf$trun_pmf)
  return(quantities)
}
cdf
```

```{r}
# write a function for cdf
# draw from uniform distribution, the value of x such

# Use the parameters, get cdf of generalized poisson, draw random number from 0 to 1

nb_theta_s <- extract(gen_pois_s_hurdle, pars = c("theta1"))
nb_lambda_s <- extract(gen_pois_s_hurdle, pars = c("lambda1"))
nb_phi_s <- extract(gen_pois_s_hurdle, pars = c("phi"))
nb_mu_s <- extract(gen_pois_s_hurdle, pars = c("mu"))
nb_psi1_s <- extract(gen_pois_s_hurdle, pars = c("psi1"))
nb_psi2_s <- extract(gen_pois_s_hurdle, pars = c("psi2"))

s_final = data.frame()
# iterate through 4000 times
for (i in 1:500) {
  
  
  # generate length
  nb_length <- rnbinom(length(s$length_minus_1), size = nb_phi_s$phi[i], 
                         prob = nb_phi_s$phi[i] / (nb_phi_s$phi[i] + nb_mu_s$mu[i]))
  
  nb_place <- c()
  max_length <- max(nb_length)
  for (length_val in nb_length) {
    nb_place <- c(nb_place, trun_hurdle(nb_psi1_s$psi1[i], nb_psi2_s$psi2[i], nb_theta_s$theta1[i], 
                                        nb_lambda_s$lambda1[i], length_val, s, max_length))

  }
  s_generated <- data.frame(nb_length, nb_place)
  s_final <- rbind(s_final, s_generated)
}

```


#### visualization

```{r}

all_df <- data.frame(nb_length = numeric(), nb_place = numeric(), n.x = numeric(), n.y = numeric())
num_iterations <- nrow(s_final) / length(s$length_minus_1)

for (i in 1:num_iterations) {
  start_index <- (i - 1) * length(s$length_minus_1) + 1
  end_index <- i * length(s$length_minus_1)
  
  subset_data <- s_final[start_index:end_index, ] %>% group_by(nb_length, nb_place) %>% count
  
  subset <- subset_data[subset_data$nb_length < 15,]
  result <- aggregate(n ~ nb_length, data = subset, FUN = sum)
  
  merged_df <- merge(subset, result, by = "nb_length")
  
  all_df <- rbind(all_df, merged_df)
}

group <- s[c("length_minus_1", "place_minus_1")]
colnames(group) <- c("nb_length", "nb_place")

group <- group %>% group_by(nb_length, nb_place) %>% count
subset <- group[group$nb_length < 15,]
result <- aggregate(n ~ nb_length, data = subset, FUN = sum)
result <- merge(subset, result, by = "nb_length")

```

```{r fig.height=400, fig.width=500}

p <- ggplot(data = all_df, aes(x = nb_place, y = n.x/n.y)) +
    geom_point(alpha = .015, position = "jitter")
    
p <- p + facet_wrap("nb_length") + geom_point(data = result %>% filter(nb_length <= 14), color = "red") + facet_wrap("nb_length")

```



### me

```{r}

gen_pois_me_hurdle = getModel("me", "Stan/gen_pois_hurdle.stan", back = T)

me <- sbc %>%
  filter(tolower(text) == "me") %>%
  filter(!is.na(place))

length(me$place)
```

#### generate quantities
```{r}

nb_theta_me <- extract(gen_pois_me_hurdle, pars = c("theta1"))
nb_lambda_me <- extract(gen_pois_me_hurdle, pars = c("lambda1"))
nb_phi_me <- extract(gen_pois_me_hurdle, pars = c("phi"))
nb_mu_me <- extract(gen_pois_me_hurdle, pars = c("mu"))

me_final = data.frame()
# iterate through 4000 times
for (i in 1:1000) {
  
  
  # generate length
  nb_length <- rnbinom(length(me$length_minus_1), size = nb_phi_me$phi[i], 
                         prob = nb_phi_me$phi[i] / (nb_phi_me$phi[i] + nb_mu_me$mu[i]))
  
  nb_place <- c()
  for (length_val in nb_length) {
    nb_place <- c(nb_place, rgenpois(1, nb_theta_me$theta1[i], nb_lambda_me$lambda1[i]))

  }
  me_generated <- data.frame(nb_length, nb_place)
  me_final <- rbind(me_final, me_generated)
}

```


#### visualization

```{r}

all_df <- data.frame(nb_length = numeric(), nb_place = numeric(), n.x = numeric(), n.y = numeric())
num_iterations <- nrow(me_final) / length(me$unitWordLen)

for (i in 1:num_iterations) {
  start_index <- (i - 1) * length(me$unitWordLen) + 1
  end_index <- i * length(me$unitWordLen)
  
  subset_data <- me_final[start_index:end_index, ] %>% group_by(nb_length, nb_place) %>% count
  
  subset <- subset_data[subset_data$nb_length < 15,]
  result <- aggregate(n ~ nb_length, data = subset, FUN = sum)
  
  merged_df <- merge(subset, result, by = "nb_length")
  
  all_df <- rbind(all_df, merged_df)
}

group <- me[c("length_minus_1", "place_minus_1")]
colnames(group) <- c("nb_length", "nb_place")

group <- group %>% group_by(nb_length, nb_place) %>% count
subset <- group[group$nb_length < 15,]
result <- aggregate(n ~ nb_length, data = subset, FUN = sum)
result <- merge(subset, result, by = "nb_length")

```

```{r fig.height=400, fig.width=500}

p <- ggplot(data = all_df, aes(x = nb_place, y = n.x/n.y)) +
    geom_point(alpha = .015, position = "jitter")
    
p <- p + facet_wrap("nb_length") + geom_point(data = result %>% filter(nb_length <= 14), color = "red") + facet_wrap("nb_length")

```


## WAIC

```{r}
library(loo)
get_waic <- function(stanfit){
  # compute WAIC from the returned object from Stan
  # the log likelihood must be named as 'log_lik'
  waic <- function(log_lik) {
    Tn <- - sum(log(colMeans(exp(log_lik))))
    fV <- sum(colMeans(log_lik^2) - colMeans(log_lik)^2)
    waic <- Tn + fV
    waic
  }
  
  stanfit %>% rstan::extract() %>% .$log_lik %>% waic()
}

get_waic(gen_pois_he)
```

```{r}
gen_pois_he = getModel("he", "Stan/gen_pois.stan", back = F)

```

```{r}
normal_pois_he = getModel("he", "Stan/He_place_given_length_NB.stan", back = F)

```

```{r}
pois_pois_he = getModel("he", "Stan/He_Pois_Pois.stan", back = F)
```



```{r}
print("generalized poisson:")
get_waic(gen_pois_he)
print("poisson:")
get_waic(normal_pois_he)
print("poisson,poisson:")
get_waic(pois_pois_he)
```

## Mixture model

### or
```{r}
or <- sbc %>%
  filter(tolower(text) == 'or') %>%
  filter(!is.na(place))

```


```{r}
mix_or <- getModel("or", "Stan/mixture_model.stan", back = F)
```


```{r}
summary(mix_or)
```

#### actual mixture


```{r}
mix_or2 <- getModel("or", "Stan/trial.stan", back = F)

summary(mix_or2)
```

#### generate quantities
```{r}
set.seed(123)
theta1 = 9.325e-02
lambda1 = 3.083e-01
theta2 = 4.300e+00
lambda2 = 1.753e-01
psi = 6.479e-01
unit_length = 9
max_length = 15
v = 0.5

# generate random value from 0 to 1, if smaller than psi, use the first part 
trun_mix <- function(theta1, lambda1, theta2, lambda2, psi, unit_length, word, max_length, v) {
  prob_list1 <- c()
  y_list <- c()
  prob_list2 <- c()
  
  
  for (y in 0:max_length) {
    prob1 <- (theta1 * (theta1 + lambda1 * y)^(y-1)) * exp(-theta1 - lambda1 * y) / factorial(y)
    prob_list1 <- c(prob_list1, prob1)  
    prob2 <- (theta2 * (theta2 + lambda2 * y)^(y-1)) * exp(-theta2 - lambda2 * y) / factorial(y)
    prob_list2 <- c(prob_list2, prob2)
    y_list <- c(y_list, y)
  }
  
  # v < psi
  cdf1 <- data.frame(Value = y_list, Proportion = prob_list1)
  cdf1$cum_sum = cumsum(cdf1$Proportion)
  F_L <- cdf1[cdf1$Value == unit_length, ]$cum_sum
  cdf1$trun_sum <- cdf1$cum_sum
  cdf1$trun_sum[cdf1$Value <= unit_length] <- cdf1$cum_sum[cdf1$Value <= unit_length] / F_L
  cdf1$trun_sum[cdf1$Value > unit_length] <- 1
  cdf1$trun_pmf <- c(cdf1$trun_sum[1], diff(cdf1$trun_sum))
  
  # v > psi
  cdf2 <- data.frame(Value = y_list, Proportion = prob_list2)
  cdf2$cum_sum = cumsum(cdf2$Proportion)
  F_L <- cdf2[cdf2$Value == unit_length, ]$cum_sum
  cdf2$trun_sum <- cdf2$cum_sum
  cdf2$trun_sum[cdf2$Value <= unit_length] <- cdf2$cum_sum[cdf2$Value <= unit_length] / F_L
  cdf2$trun_sum[cdf2$Value > unit_length] <- 1
  cdf2$trun_pmf <- c(cdf2$trun_sum[1], diff(cdf2$trun_sum))
  
  if (v < psi) {
    quantities <- sample(cdf1$Value, size = 1, replace = TRUE, prob = cdf1$trun_pmf)
  }
  else {
    quantities <- sample(cdf2$Value, size = 1, replace = TRUE, prob = cdf2$trun_pmf)
  }
  return(quantities)
}

```

```{r}
# write a function for cdf
# draw from uniform distribution, the value of x such

# Use the parameters, get cdf of generalized poisson, draw random number from 0 to 1

nb_theta1_or <- rstan::extract(mix_or2, pars = c("theta1"))
nb_lambda1_or <- rstan::extract(mix_or2, pars = c("lambda1"))
nb_theta2_or <- rstan::extract(mix_or2, pars = c("theta2"))
nb_lambda2_or <- rstan::extract(mix_or2, pars = c("lambda2"))

nb_phi1_or <- rstan::extract(mix_or2, pars = c("phi1"))
nb_mu1_or <- rstan::extract(mix_or2, pars = c("mu1"))
nb_phi2_or <- rstan::extract(mix_or2, pars = c("phi2"))
nb_mu2_or <- rstan::extract(mix_or2, pars = c("mu2"))
nb_psi_or <- rstan::extract(mix_or2, pars = c("psi"))

## generate a v for each length, then divide them into corresponding group then go to cdf,  
or_final = data.frame()
# iterate through 4000 times
for (j in 1:1000) {
  
  nb_length <- c()
  li <- c()
  gi <- c()
  for (i in 1:length(or$length_minus_1)) {
    v <- runif(1, 0, 1)      # generate a value
    psi <- nb_psi_or$psi[i]
    if (v < psi) {
      len1 <- rnbinom(1, size = nb_phi1_or$phi1[i], 
                        prob = nb_phi1_or$phi1[i] / (nb_phi1_or$phi1[i] + nb_mu1_or$mu1[i]))
      nb_length1 <- c(nb_length1, len1)
      max_length1 <- max(nb_length1)
      li <- c(li, i)
      
    } else {
      len2 <- rnbinom(1, size = nb_phi2_or$phi2[i], 
                            prob = nb_phi2_or$phi2[i] / (nb_phi2_or$phi2[i] + nb_mu2_or$mu2[i]))
      nb_length2 <- c(nb_length2, len2)
      max_length2 <- max(nb_length2)
      gi <- c(gi, i)
      }
  }

  nb_place1 <- c()
  for (k in 1:length(nb_length1)){
    nb_place1 <- c(nb_place1, trun_mix(nb_theta1_or$theta1[li[k]], nb_lambda1_or$lambda1[li[k]],
                                       nb_theta2_or$theta2[li[k]], nb_lambda2_or$lambda2[li[k]],
                                       psi, nb_length1[k], or, max_length))
  }
  
  nb_place2 <- c()
  for (k in 1:length(nb_length1)){
    nb_place1 <- c(nb_place1, trun_mix(nb_theta1_or$theta1[li[k]], nb_lambda1_or$lambda1[li[k]],
                                       nb_theta2_or$theta2[li[k]], nb_lambda2_or$lambda2[li[k]],
                                       psi, nb_length1[k], or, max_length))
  }
  
  nb_length <- c(nb_length1, nb_length2)
  
  
  
  or_generated <- data.frame(nb_length, nb_place)
  or_final <- rbind(or_final, or_generated)
}



  if (v < psi) {
    for (length_val in nb_length) {
      nb_place <- c(nb_place, trun_mix(nb_theta1_or$theta1[i], nb_lambda1_or$lambda1[i],
                                       nb_theta2_or$theta2[i], nb_lambda2_or$lambda2[i],
                                       psi, length_val, or, max_length, v))
    }
  }  
```

#### visualization

```{r}

all_df <- data.frame(nb_length = numeric(), nb_place = numeric(), n.x = numeric(), n.y = numeric())
num_iterations <- nrow(or_final) / length(or$unitWordLen)

for (i in 1:num_iterations) {
  start_index <- (i - 1) * length(or$unitWordLen) + 1
  end_index <- i * length(or$unitWordLen)
  
  subset_data <- or_final[start_index:end_index, ] %>% group_by(nb_length, nb_place) %>% count
  
  subset <- subset_data[subset_data$nb_length < 15,]
  result <- aggregate(n ~ nb_length, data = subset, FUN = sum)
  
  merged_df <- merge(subset, result, by = "nb_length")
  
  all_df <- rbind(all_df, merged_df)
}

group <- or[c("length_minus_1", "place_minus_1")]
colnames(group) <- c("nb_length", "nb_place")

group <- group %>% group_by(nb_length, nb_place) %>% count
subset <- group[group$nb_length < 15,]
result <- aggregate(n ~ nb_length, data = subset, FUN = sum)
result <- merge(subset, result, by = "nb_length")

```

```{r fig.height=400, fig.width=500}

p <- ggplot(data = all_df, aes(x = nb_place, y = n.x/n.y)) +
    geom_point(alpha = .015, position = "jitter")
    
p <- p + facet_wrap("nb_length") + geom_point(data = result %>% filter(nb_length <= 14), color = "red") + facet_wrap("nb_length")

```






## Regression



```{r}
he <- sbc %>%
  filter(tolower(text) == 'he') %>%
  filter(!is.na(place))

```


```{r}
he_length <- list()
length <- c()
for (i in seq(sort(unique(he$length_minus_1)))) {
   he_length[[i]] = he %>% filter(length_minus_1 == sort(unique(he$length_minus_1))[i])
   length <- c(length, sort(unique(he$length_minus_1))[i])
}
length_df <- data.frame(length)
length_df
```


```{r}
getModel_reg = function(file_path, data_raw, back = F){
  
  if(!back){
    data_input <- list(
      N = nrow(data_raw),
      place = pull(data_raw, place_minus_1),
      unit_length = pull(data_raw, length_minus_1)
    )
  } else {
    data_input <- list(
      N = nrow(data),
      place = pull(data_raw, length_minus_1) - pull(data_raw, place_minus_1),
      unit_length = pull(data_raw, length_minus_1)
    )
  }

  stan(
    file = file_path,
    data = data_input,
    chain = 4,
    cores = getOption("mc.cores", 4)
  )
}

file_path = 'Stan/regre_gen.stan'
length_list = he_length
regre_gen_df <- function(df, length_list, word, file_path, back = F) {
  thetas <- c()
  lambdas <- c()
  words <- rep(word, length(length_list))
  for (i in length_list) {
    stan_model <- getModel_reg(file_path, i, back = F)
    theta <- summary(stan_model)[[1]][1]
    thetas <- c(thetas, theta)
    lambda <- summary(stan_model)[[1]][2]
    lambdas <- c(lambdas, lambda)
  }
  df$lambda <- lambdas
  df$theta <- thetas
  df$words <- words
  
  return(df)
}

stan_model <- getModel_reg(file_path, length_list[[19]], back = F)
theta <- summary(stan_model)[[1]][1]
thetas <- c(thetas, theta)
lambda <- summary(stan_model)[[1]][2]
lambdas <- c(lambdas, lambda)



```

```{r}
he_reg_df <- regre_gen_df(length_df, he_length, 'he', 'Stan/regre_gen.stan', back = F)
```

```{r}
num_rows <- nrow(length_df)
# Remove the last row from the dataframe
length_df <- length_df[-num_rows, ]
length_df <- as.data.frame(length_df)
length_df$lambda <- lambdas
length_df$theta <- thetas

length_df
```

```{r}
plot(length_df$lambda, length_df$length_df)
plot(length_df$theta, length_df$length_df)
```



```{r}
model <- lm(length_df ~ lambda, data = length_df)

summary(model)
plot(model)
```


```{r}
model <- lm(length_df ~ theta, data = length_df)

summary(model)
plot(model)

```

### Regression within stan

```{r}
he <- sbc %>%
  filter(tolower(text) == 'he') %>%
  filter(!is.na(place))

```


```{r}
getModel = function(word, file_path, back = F){
  data_raw <- sbc %>%
    filter(tolower(text) == word) %>%
    filter(!is.na(place))
  
  if(!back){
    data_input <- list(
      N = nrow(data_raw),
      place = pull(data_raw, place_minus_1),
      unit_length = pull(data_raw, length_minus_1)
    )
  } else {
    data_input <- list(
      N = nrow(data_raw),
      place = pull(data_raw, length_minus_1) - pull(data_raw, place_minus_1) + 1,
      unit_length = pull(data_raw, length_minus_1)
    )
  }

  stan(
    file = file_path,
    data = data_input,
    chain = 4,
    cores = getOption("mc.cores", 4)
  )
}
```

```{r}
he_regre <- getModel("he", "Stan/Regression.stan", back = F)
```

```{r}
summary(he_regre)
```



