---
title: "systematic"
author: "Lu Liu"
date: "2024-02-29"
output: html_document
---

```{r setup, echo=FALSE}
library(knitr)
# set global chunk options: images will be 7x5 inches
knitr::opts_chunk$set(fig.width=7, fig.height=5)
options(digits = 4)
```

```{r, include=FALSE}
# for debugging latex
options(tinytex.verbose = TRUE)
```

# Loading Packages
```{r}
library(tidyverse)
library(rstan)
library(tidyr)
library(HMMpa)
library(boot)
```

# Loading Data
```{r}
setwd("~/Desktop/Projects/sb corpus")
load("/Users/lu//Desktop/Projects/sb corpus/sbc.Rdata")
#load("G:\\共用雲端硬碟\\Prosody & Units in Dialogue\\Staircases\\reorganised_code\\sbc.Rdata")
```

```{r}
sbc$place_minus_1 = sbc$place - 1
sbc$length_minus_1 = sbc$unitWordLen - 1
```

# Necessary functions

### Get model 
```{r}
getModel <- function(word, file_path, back = F){
  data_raw <- sbc %>%
    filter(tolower(text) == word) %>%
    filter(!is.na(place))
  
  if(!back){
    data_input <- list(
      N = nrow(data_raw),
      place = pull(data_raw, place_minus_1),
      unit_length = pull(data_raw, length_minus_1)
    )
  } else {
    data_input <- list(
      N = nrow(data_raw),
      place = pull(data_raw, length_minus_1) - pull(data_raw, place_minus_1),
      unit_length = pull(data_raw, length_minus_1)
    )
  }

  stan(
    file = file_path,
    data = data_input,
    chain = 4,
    cores = getOption("mc.cores", 4)
  )
}
```


### CDF for Generalized Poisson
```{r}
set.seed(123)
theta = 0.7823
lambda = 0.3263
unit_length = 9


trun_rgen <- function(theta, lambda, unit_length, word, max_length) {
  prob_list <- c()
  y_list <- c()
  for (y in 0:max_length) {
    prob <- (theta * (theta + lambda * y)^(y-1)) * exp(-theta - lambda * y) / factorial(y)
    prob_list <- c(prob_list, prob)
    y_list <- c(y_list, y)
  }
  
  cdf <- data.frame(Value = y_list, Proportion = prob_list)
  cdf$cum_sum = cumsum(cdf$Proportion)
  
  F_L <- cdf[cdf$Value == unit_length, ]$cum_sum
  cdf$trun_sum <- cdf$cum_sum
  cdf$trun_sum[cdf$Value <= unit_length] <- cdf$cum_sum[cdf$Value <= unit_length] / F_L

  cdf$trun_sum[cdf$Value > unit_length] <- 1
  
  cdf$trun_pmf <- c(cdf$trun_sum[1], diff(cdf$trun_sum))
  
  quantities <- sample(cdf$Value, size = 1, replace = TRUE, prob = cdf$trun_pmf)
  return(quantities)
}

```


### Generate Quantities For Generalized Poisson

```{r}
Gen_Pois_Quantities <- function(model, word, back = F){
  
  nb_theta <- extract(model, pars = c("theta"))
  nb_lambda <- extract(model, pars = c("lambda"))
  nb_phi <- extract(model, pars = c("phi"))
  nb_mu <- extract(model, pars = c("mu"))

  final = data.frame()
  # iterate through 4000 times
  for (i in 1:200) {
    # generate length
    nb_length <- rnbinom(length(word$length_minus_1), size = nb_phi$phi[i], 
                           prob = nb_phi$phi[i] / (nb_phi$phi[i] + nb_mu$mu[i]))
    
    nb_place <- c()
    max_length <- max(nb_length)
    for (length_val in nb_length) {
      nb_place <- c(nb_place, trun_rgen(nb_theta$theta[i], nb_lambda$lambda[i], length_val, word, max_length))
  
    }
    if (back == T) {
      nb_place <- nb_length - nb_place
    }
    generated <- data.frame(nb_length, nb_place)
    final <- rbind(final, generated)
  }
  return(final)
}
```

### CDF for Mixture Model

```{r}
trun_mix <- function(theta, lambda, unit_length, max_length) {
  prob_list <- c()
  y_list <- c()

  for (y in 0:max_length) {
    prob <- (theta * (theta + lambda * y)^(y-1)) * exp(-theta - lambda * y) / factorial(y)
    prob_list <- c(prob_list, prob)  
    y_list <- c(y_list, y)
  }
  
  cdf <- data.frame(Value = y_list, Proportion = prob_list)
  cdf$cum_sum = cumsum(cdf$Proportion)
  F_L <- cdf[cdf$Value == unit_length, ]$cum_sum
  cdf$trun_sum <- cdf$cum_sum
  cdf$trun_sum[cdf$Value <= unit_length] <- cdf$cum_sum[cdf$Value <= unit_length] / F_L
  cdf$trun_sum[cdf$Value > unit_length] <- 1
  cdf$trun_pmf <- c(cdf$trun_sum[1], diff(cdf$trun_sum))
  
  
  quantities <- sample(cdf$Value, size = 1, replace = TRUE, prob = cdf$trun_pmf)

  return(quantities)
}
```



### Generate Quantities For Mixture Model

```{r}
Mix_Pois_Quantities <- function(model, word) {
  nb_theta1 <- rstan::extract(model, pars = c("theta1"))
  nb_lambda1 <- rstan::extract(model, pars = c("lambda1"))
  nb_theta2 <- rstan::extract(model, pars = c("theta2"))
  nb_lambda2 <- rstan::extract(model, pars = c("lambda2"))
  
  nb_phi1 <- rstan::extract(model, pars = c("phi1"))
  nb_mu1 <- rstan::extract(model, pars = c("mu1"))
  nb_phi2 <- rstan::extract(model, pars = c("phi2"))
  nb_mu2 <- rstan::extract(model, pars = c("mu2"))
  nb_psi <- rstan::extract(model, pars = c("psi"))
  
  ## generate a v for each length, then divide them into corresponding group then go to cdf,  
  final = data.frame()
  # iterate through 4000 times
  for (j in 1:200) {
    li <- c()
    gi <- c()
    nb_length1 <- c()
    nb_length2 <- c()
    for (i in 1:length(nb_psi$psi)) {
      v <- runif(1, 0, 1)      # generate a value
      psi <- nb_psi$psi[i]
      if (v < psi) {
        len1 <- rnbinom(1, size = nb_phi1$phi1[i], 
                          prob = nb_phi1$phi1[i] / (nb_phi1$phi1[i] + nb_mu1$mu1[i]))
        nb_length1 <- c(nb_length1, len1)
        max_length1 <- max(nb_length1)
        li <- c(li, i)
        
      } else {
        len2 <- rnbinom(1, size = nb_phi2$phi2[i], 
                              prob = nb_phi2$phi2[i] / (nb_phi2$phi2[i] + nb_mu2$mu2[i]))
        nb_length2 <- c(nb_length2, len2)
        max_length2 <- max(nb_length2)
        gi <- c(gi, i)
        }
    }
  
    nb_place1 <- c()
    for (k in 1:length(nb_length1)){
      nb_place1 <- c(nb_place1, trun_mix(nb_theta1$theta1[li[k]], nb_lambda1$lambda1[li[k]],
                                         nb_length1[k], max_length1))
    }
    
    nb_place2 <- c()
    for (k in 1:length(nb_length2)){
      nb_place2 <- c(nb_place2, trun_mix(nb_theta2$theta2[gi[k]], nb_lambda2$lambda2[gi[k]],
                                         nb_length2[k], max_length2))
    }
    
    nb_place2 <- nb_length2 - nb_place2
    
    nb_length <- c(nb_length1, nb_length2)
    nb_place <- c(nb_place1, nb_place2)
    
    
    generated <- data.frame(nb_length, nb_place)
    final <- rbind(final, generated)
  }
  return(final)
}
```



### CDF for hurdle model

```{r}
trun_hurdle <- function(theta, lambda, psi_intercept, psi_slope, alpha = NULL, unit_length, word, max_length, hurdle) {
  prob_list <- c()
  y_list <- c()
  psi <- inv.logit(unit_length*psi_slope + psi_intercept)
  
  if (hurdle == 0) {
    prob_list <- c(prob_list, psi)
    y_list <- c(y_list, 0)
    for (y in 1:max_length) {
      prob <- (1-psi)* ((theta * (theta + lambda * y)^(y-1)) * exp(-theta - lambda * y) / factorial(y))/ 
      (1 - (theta * theta^(-1) * exp(-theta)))

    prob_list <- c(prob_list, prob)
    y_list <- c(y_list, y)
    }
  }
  else {
    prob_list <- c(prob_list, alpha, psi)
    y_list <- c(y_list, 0, 1)
    
    lpos_0 <- (theta * theta^(-1) * exp(-theta))
    lpos_1 <- (theta * exp(-theta - lambda))
    
    for (y in 2:max_length) {
      prob <- (1-alpha-psi)* ((theta * (theta + lambda * y)^(y-1)) * exp(-theta - lambda * y) /
                                factorial(y))/(1 - lpos_0 - lpos_1)
  
      prob_list <- c(prob_list, prob)
      y_list <- c(y_list, y)
    }    
  }
  
  cdf <- data.frame(Value = y_list, Proportion = prob_list)
  cdf$cum_sum = cumsum(cdf$Proportion)
  
  F_L <- cdf[cdf$Value == unit_length, ]$cum_sum
  cdf$trun_sum <- cdf$cum_sum
  cdf$trun_sum[cdf$Value <= unit_length] <- cdf$cum_sum[cdf$Value <= unit_length] / F_L

  cdf$trun_sum[cdf$Value > unit_length] <- 1
  
  cdf$trun_pmf <- c(cdf$trun_sum[1], diff(cdf$trun_sum))
  
  quantities <- sample(cdf$Value, size = 1, replace = TRUE, prob = cdf$trun_pmf)
  return(quantities)
}
```


### Generate Quantities For Hurdle Model

```{r}
Hurdle_Pois_Quantities <- function(model, word, back = F, hurdle) {
  nb_theta <- rstan::extract(model, pars = c("theta"))
  nb_lambda <- rstan::extract(model, pars = c("lambda"))
  nb_phi <- rstan::extract(model, pars = c("phi"))
  nb_mu <- rstan::extract(model, pars = c("mu"))
  
  nb_psi_inter <- rstan::extract(model, pars = c("psi_intercept"))
  nb_psi_slope <- rstan::extract(model, pars = c("psi_slope"))

  if (hurdle == 1) {
    nb_alpha <- rstan::extract(model, pars = c("alpha"))
  }
  
  final = data.frame()
  
  for (i in 1:200) {
    nb_length <- rnbinom(length(word$length_minus_1), size = nb_phi$phi[i], 
                         prob = nb_phi$phi[i] / (nb_phi$phi[i] + nb_mu$mu[i]))
    nb_place <- c()
    max_length <- max(nb_length)
    
    if (hurdle == 1) {
      alpha = nb_alpha$alpha[i]
    }
    else {
      alpha = NULL
    }
    for (length_val in nb_length) {
      nb_place <- c(nb_place, trun_hurdle(nb_theta$theta[i], nb_lambda$lambda[i], 
                                        nb_psi_inter$psi_intercept[i],
                                        nb_psi_slope$psi_slope[i],
                                        alpha, length_val, word, max_length, hurdle))
      }
    if (back == T) {
      nb_place <- nb_length - nb_place
    }
    generated <- data.frame(nb_length, nb_place)
    final <- rbind(final, generated)
  }
  return(final)
}
```


### DF for visualization
```{r}
df_visual <- function(quantities, word) {
  all_df <- data.frame(nb_length = numeric(), nb_place = numeric(), n.x = numeric(), n.y = numeric())
  num_iterations <- nrow(quantities) / length(word$length_minus_1)
  
  for (i in 1:num_iterations) {
    start_index <- (i - 1) * length(word$length_minus_1) + 1
    end_index <- i * length(word$length_minus_1)
    
    subset_data <- quantities[start_index:end_index, ] %>% group_by(nb_length, nb_place) %>% count
    
    subset <- subset_data[subset_data$nb_length < 15,]
    result <- aggregate(n ~ nb_length, data = subset, FUN = sum)
    
    merged_df <- merge(subset, result, by = "nb_length")
    
    all_df <- rbind(all_df, merged_df)
  }
  
  group <- word[c("length_minus_1", "place_minus_1")]
  colnames(group) <- c("nb_length", "nb_place")
  
  group <- group %>% group_by(nb_length, nb_place) %>% count #() %>% rename(count = n)
  subset <- group[group$nb_length < 15,]
  result <- aggregate(n ~ nb_length, data = subset, FUN = sum)
  result <- merge(subset, result, by = "nb_length")
  
  return(list(all_df = all_df, result = result))
}
```


### plotting 

```{r}
plotting <- function(all_df, result, word) {
  
  labels_map <- result %>% 
    group_by(nb_length) %>% 
    summarise(n.y = unique(n.y)) %>%
    deframe()  
  custom_labeller <- function(nb_length) {
    sapply(nb_length, function(x) paste(x, "size:", labels_map[x]))
  }
  
  p <- ggplot(data = all_df, aes(x = nb_place, y = n.x/n.y)) +
    geom_point(alpha = .015, position = "jitter")
    
  p <- p + facet_wrap("nb_length", labeller = as_labeller(custom_labeller)) + 
    geom_point(data = result %>% filter(nb_length <= 14), color = "red") +
    labs(title = word) +
    theme(plot.title = element_text(hjust = 0.5)) + 
    xlab("place") +  
    ylab("Count Proportion")   
  
  return(p)
}
```

### WAIC

```{r}
library(loo)
get_waic <- function(stanfit){
  # compute WAIC from the returned object from Stan
  # the log likelihood must be named as 'log_lik'
  waic <- function(log_lik) {
    Tn <- - mean(log(colMeans(exp(log_lik))))
    s <- ncol(log_lik)
    fV <- (sum(colMeans(log_lik^2) - colMeans(log_lik)^2))*(s/(s-1)) #s/s-1 then multiply whole thing by two 
    waic <- 2*(Tn + fV)
    waic
  }
  
  stanfit %>% rstan::extract() %>% .$log_lik %>% waic()
}

```

# Checking frontness

find 

```{r}
front_or_back <- function(word) {
  word_back <- word %>%
    group_by(length_minus_1) %>%
    summarise(proportion = sum(place_minus_1 == length_minus_1, na.rm = TRUE) / n()) %>%
    arrange(length_minus_1)
  
  word_front <- word %>%
    group_by(length_minus_1) %>% 
    summarise(proportion = sum(place_minus_1 == 0, na.rm = TRUE) / n()) %>% # Count matching values
    arrange(length_minus_1) 
  
  back_slope <- lm(word_back$proportion ~ word_back$length_minus_1)
  front_slope <- lm(word_front$proportion ~ word_front$length_minus_1)
  
  return(list(back = back_slope, front = front_slope))
}
```

```{r}
front_back_when <- front_or_back(when)
(back_slope <- front_back_when$back)
(front_slope <- front_back_when$front)
```


```{r}
when_back <- when %>%
  group_by(length_minus_1) %>% 
  summarise(proportion = sum(place_minus_1 == length_minus_1, na.rm = TRUE) / n()) %>% # Calculate proportion of matching values
  arrange(length_minus_1)

when_back$length_minus_1
when_backresult <- when_back$proportion
when_backresult
```
place count / count of all iu at same length, relatively stabler than the following one. 

17  6  3  2  4  4  0  1  0  1  1  1  0  0  0  0  0  0  0


```{r}
when_front <- when %>%
  group_by(length_minus_1) %>% 
  summarise(proportion = sum(place_minus_1 == 0, na.rm = TRUE) / n()) %>% # Count matching values
  arrange(length_minus_1) 

when_frontresult <- when_front$count
when_frontresult

ggplot(data = data.frame(prop = c(when_back$proportion / max(when_back$proportion),
                                  when_front$proportion / max(when_front$proportion)),
                         value = c(1:length(when_back$proportion), 1:length(when_front$proportion)),
                         fb = rep(c("back", "front"), each = c(length(when_back$proportion), length(when_front$proportion)))),
       aes(x = value, y = prop, col = fb)) +
  geom_point()
```


```{r}
when_summary <- when %>%
  group_by(length_minus_1, place_minus_1) %>%
  summarise(count = n(), .groups = "drop") %>%
  arrange(length_minus_1, desc(count)) %>%
  group_by(length_minus_1) %>%
  slice(1) %>%
  select(length_minus_1, place_minus_1, count)

when_summary <- when_summary %>% filter(length_minus_1 <= 14)
when_summary$mode_percentage <- (1+when_summary$place_minus_1)/(1+when_summary$length_minus_1)
print(when_summary)
```


```{r}
lm(when_summary$place_minus_1~when_summary$length_minus_1)
``` 


```{r}
plot(when_summary$length_minus_1, when_summary$place_minus_1)
```
```{r}
way <- sbc %>%
  filter(tolower(text) == 'way') %>%
  filter(!is.na(place))
```

```{r}
way_summary <- way %>%
  group_by(length_minus_1, place_minus_1) %>%
  summarise(count = n(), .groups = "drop") %>%
  arrange(length_minus_1, desc(count)) %>%
  group_by(length_minus_1) %>%
  slice(1) %>%
  select(length_minus_1, place_minus_1, count)
way_summary <- way_summary %>% filter(length_minus_1 <= 14)
way_summary$mode_percentage <- (1+way_summary$place_minus_1)/(1+way_summary$length_minus_1)
print(way_summary)

mean(way_summary$mode_percentage > 0.5)
```

```{r}
plot(way_summary$length_minus_1, way_summary$place_minus_1)
```
```{r}
lm(way_summary$place_minus_1~way_summary$length_minus_1)
``` 
### Define function (fix mode)
```{r}
check_back <- function(word) {
  summary <- word %>%
  group_by(length_minus_1, place_minus_1) %>%
  summarise(count = n(), .groups = "drop") %>%
  arrange(length_minus_1, desc(count)) %>%
  group_by(length_minus_1) %>%
  slice(1) %>%
  select(length_minus_1, place_minus_1, count)
  summary <- summary %>% filter(length_minus_1 <= 14)
  summary$mode_percentage <- (1+summary$place_minus_1)/(1+summary$length_minus_1)
  
  criteria <- mean(summary$mode_percentage > 0.5)
  #print(criteria)
  if (criteria > 0.5) {
    return(T)
  }
  else {
    return(F)
  }
}
```

```{r}
check_back(way)
```

```{r}
check_back(when)
```

# Try out words
# Define a function for different model visualizations

```{r}
generate_vis <- function(word_str, model_type = "gen"){
  word <- sbc %>%
    filter(tolower(text) == word_str) %>%
    filter(!is.na(place))
  cri <- check_back(word)
  print(cri)
  if (model_type == "gen"){
    model_word = getModel(word_str, "Stan/gen_pois.stan", back = cri)
    word_final = Gen_Pois_Quantities(model_word, word, back = cri)
  }
  else if (model_type == "mix"){
    model_word = getModel(word_str, "Stan/mixture_model.stan", back = cri)
    word_final = Mix_Pois_Quantities(model_word, word)
  }
  else if (model_type == "hur0") {
    model_word = getModel(word_str, "Stan/gen_pois_hurdle.stan", back = cri)
    word_final = Hurdle_Pois_Quantities(model_word, word, back = cri, hurdle = 0)
  }
  ## Need to check
  else if (model_type == "hur1") {
    model_word = getModel(word_str, "Stan/gen_pois_hurdle.stan", back = cri)
    word_final = Hurdle_Pois_Quantities(model_word, word, back = cri, hurdle = 1)
  }
  output <- df_visual(word_final, word)
  all_df <- output$all_df
  result <- output$result
  
  p <- plotting(all_df, result, word_str)
  return (list(p, model_word, word_final))
}

```


## 1 An
### Gen

```{r}
an <- sbc %>%
  filter(tolower(text) == 'an') %>%
  filter(!is.na(place))
```

```{r}
check_back(an)
```

```{r}
gen_pois_an = getModel("an", "Stan/gen_pois.stan", back = T)
```

```{r}
an_final = Gen_Pois_Quantities(gen_pois_an, an, back = T)
```

```{r}
output <- df_visual(an_final, an)
all_df <- output$all_df
result <- output$result
```

```{r}
p1 <- plotting(all_df, result)
print(p1)
```


### Mix
```{r}
mix_an = getModel("an", "Stan/mixture_model.stan", back = F)
```

```{r}
an_final_mix = Mix_Pois_Quantities(mix_an, an)
```

```{r}
output <- df_visual(an_final_mix, an)
all_df <- output$all_df
result <- output$result
```

```{r}
p2 <- plotting(all_df, result)
print(p2)
```
`                                                                                                                 

## 1.5

```{r}
and <- sbc %>%
  filter(tolower(text) == 'and') %>%
  filter(!is.na(place))
```

```{r}
cri <- check_back(and)
cri
```


```{r}
gen_pois_and = getModel("and", "Stan/gen_pois.stan", back = F)
```

```{r}
and_final = Gen_Pois_Quantities(gen_pois_and, and, back = F)
```

```{r}
output <- df_visual(and_final, and)
all_df <- output$all_df
result <- output$result
```

```{r}
# logistic, place being 1 or not, vary hurdle by length? try hurdle first 
p3 <- plotting(all_df, result)
print(p3)
```

### Hurdle 

```{r}
hurdle1_and = getModel("and", "Stan/gen_pois_hurdle.stan", back = F)
```

```{r}
and_final_hurdle = Hurdle_Pois_Quantities(hurdle1_and, and, hurdle = 0, back = F)
```

```{r}
output <- df_visual(and_final_hurdle, and)
all_df <- output$all_df
result <- output$result

result
```

change back

```{r}
# logistic, place being 1 or not, vary hurdle by length? try hurdle first 
p3_5 <- plotting(all_df, result, 'and')
print(p3_5)
```

## 2 For


```{r}
For <- sbc %>%
  filter(tolower(text) == 'for') %>%
  filter(!is.na(place))
```

```{r}
cri <- check_back(For)
cri
```

### Mix
```{r}
mix_for = getModel("for", "Stan/mixture_model.stan", back = F)
```

```{r}
for_final_mix = Mix_Pois_Quantities(mix_for, For)
```

```{r}
output <- df_visual(for_final_mix, For)
all_df <- output$all_df
result <- output$result
```

```{r}
p4 <- plotting(all_df, result, 'for')
print(p4)
```


## Last (Failed)
### Gen
```{r}
# set initial values to force stan to start 
# https://discourse.mc-stan.org/t/how-to-define-initial-values-in-stan-in-r/16855
gen_pois_last = getModel("last", "Stan/gen_pois.stan", back = T)
```

```{r}
last_final = Gen_Pois_Quantities(gen_pois_last, last, back = T)
```

```{r}
output <- df_visual(last_final, last)
all_df <- output$all_df
result <- output$result
```

```{r}
p5 <- plotting(all_df, result)
print(p5)
```

## 3 With

```{r}
with <- sbc %>%
  filter(tolower(text) == 'with') %>%
  filter(!is.na(place))
```

```{r}
cri <- check_back(with)
cri
```


### Gen
```{r}
gen_pois_with = getModel("with", "Stan/gen_pois.stan", back = T)
```

```{r}
with_final = Gen_Pois_Quantities(gen_pois_with, with, back = T)
```

```{r}
output <- df_visual(with_final, with)
all_df <- output$all_df
result <- output$result
```

```{r}
p6 <- plotting(all_df, result)
print(p6)
```

## 4 Should

```{r}
should <- sbc %>%
  filter(tolower(text) == 'should') %>%
  filter(!is.na(place))
```

```{r}
cri <- check_back(should)
cri
```


### Gen
```{r}
# try hurdle
gen_pois_should = getModel("should", "Stan/gen_pois.stan", back = F)
```

```{r}
should_final = Gen_Pois_Quantities(gen_pois_should, should, back = F)
```

```{r}
output <- df_visual(should_final, should)
all_df <- output$all_df
result <- output$result
```

```{r}
p7 <- plotting(all_df, result)
print(p7)
```

## 5 It

```{r}
it <- sbc %>%
  filter(tolower(text) == 'it') %>%
  filter(!is.na(place))
```

```{r}
cri <- check_back(it)
cri
```


### Mix
```{r}
mix_it = getModel("it", "Stan/mixture_model.stan", back = F)
```
```{r}
get_waic(mix_it)
```


```{r}
gen_it = getModel("it", "Stan/gen_pois.stan", back = F)
```
```{r}
get_waic(gen_it)
```

```{r}
it_final_mix = Mix_Pois_Quantities(mix_it, it)
```

```{r}
output <- df_visual(it_final_mix, it)
all_df <- output$all_df
result <- output$result
```

```{r}
p8 <- plotting(all_df, result)
print(p8)
```

## 6 Because

### Gen

```{r}
because <- sbc %>%
  filter(tolower(text) == 'because') %>%
  filter(!is.na(place))
```

```{r}
cri <- check_back(because)
cri
```


```{r}
# try hurdle
gen_pois_because= getModel("because", "Stan/gen_pois.stan", back = F)
```

```{r}
because_final = Gen_Pois_Quantities(gen_pois_because, because, back = F)
```

```{r}
output <- df_visual(because_final, because)
all_df <- output$all_df
result <- output$result
```

```{r}
p9 <- plotting(all_df, result, 'because')
print(p9)
```

## 7 her

### Gen

```{r}
her <- sbc %>%
  filter(tolower(text) == 'her') %>%
  filter(!is.na(place))
```

```{r}
cri <- check_back(her)
cri
```

```{r}
# try hurdle
gen_pois_her= getModel("her", "Stan/gen_pois.stan", back = T)
```

```{r}
her_final = Gen_Pois_Quantities(gen_pois_her, because, back = T)
```

```{r}
output <- df_visual(her_final, her)
all_df <- output$all_df
result <- output$result
```

```{r}
p10 <- plotting(all_df, result)
print(p10)
```

## 8 let

### Gen

```{r}
let <- sbc %>%
  filter(tolower(text) == 'let') %>%
  filter(!is.na(place))
```

```{r}
cri <- check_back(let)
cri
```

```{r}
# try hurdle
gen_pois_let= getModel("let", "Stan/gen_pois.stan", back = F)
```

```{r}
let_final = Gen_Pois_Quantities(gen_pois_let, let, back = F)
```

```{r}
output <- df_visual(let_final, let)
all_df <- output$all_df
result <- output$result
```

```{r}
p11 <- plotting(all_df, result)
print(p11)
```

## 9 them

### Gen

```{r}
them <- sbc %>%
  filter(tolower(text) == 'them') %>%
  filter(!is.na(place))
```

```{r}
cri <- check_back(them)
cri
```

```{r}
# try hurdle
gen_pois_them = getModel("them", "Stan/gen_pois.stan", back = T)
```

```{r}
them_final = Gen_Pois_Quantities(gen_pois_them, them, back = T)
```

```{r}
output <- df_visual(them_final, them)
all_df <- output$all_df
result <- output$result
```

```{r}
p12 <- plotting(all_df, result, 'them')
print(p12)
```


## 10 when

### Gen

not suitable for the models we're doing. (expection)
Try mixture to see? logitics

```{r}
when <- sbc %>%
  filter(tolower(text) == 'when') %>%
  filter(!is.na(place))
```

```{r}
cri <- check_back(when)
cri
```

```{r}
# try hurdle
gen_pois_when = getModel("when", "Stan/gen_pois.stan", back = F)
```

```{r}
when_final = Gen_Pois_Quantities(gen_pois_when, when, back = F)
```

```{r}
output <- df_visual(when_final, when)
all_df <- output$all_df
result <- output$result
```

```{r}
p13 <- plotting(all_df, result, 'when')
print(p13)
```

### Hurdle

```{r}
# try hurdle
hurdle1_when = getModel("when", "Stan/gen_pois_hurdle.stan", back = F)
```

```{r}
when_hurdle = Hurdle_Pois_Quantities(hurdle1_when, when, back = F, hurdle = 0)
```

```{r}
output <- df_visual(when_hurdle, when)
all_df <- output$all_df
result <- output$result
```

```{r}
p13 <- plotting(all_df, result, 'when')
print(p13)
```



## 11 year

### Gen

```{r}
year <- sbc %>%
  filter(tolower(text) == 'year') %>%
  filter(!is.na(place))
```

```{r}
cri <- check_back(year)
cri
```


```{r}
gen_pois_year = getModel("year", "Stan/gen_pois.stan", back = T)
```

```{r}
year_final = Gen_Pois_Quantities(gen_pois_year, year, back = T)
```

```{r}
output <- df_visual(year_final, year)
all_df <- output$all_df
result <- output$result
```

```{r}
p14 <- plotting(all_df, result)
print(p14)
```

## 12 em

### Gen

hurdle for final position 

```{r}
em <- sbc %>%
  filter(tolower(text) == 'em') %>%
  filter(!is.na(place))
```

```{r}
cri <- check_back(em)
cri
```

```{r}
gen_pois_em = getModel("em", "Stan/gen_pois.stan", back = T)
```

```{r}
em_final = Gen_Pois_Quantities(gen_pois_em, em, back = T)
```

```{r}
output <- df_visual(em_final, em)
all_df <- output$all_df
result <- output$result
```

```{r}
p15 <- plotting(all_df, result, 'em')
print(p15)
```


### Hurdle

```{r}
hurdle1_em = getModel("em", "Stan/gen_pois_hurdle.stan", back = T)
```

```{r}
em_hurdle = Hurdle_Pois_Quantities(hurdle1_em, em, back = T, hurdle = 0)
```

```{r}
output <- df_visual(em_hurdle, em)
all_df <- output$all_df
result <- output$result
```

```{r}
p15_5 <- plotting(all_df, result, 'em')
print(p15_5)
```
## 13 him

### Gen

Hurdle

```{r}
him <- sbc %>%
  filter(tolower(text) == 'him') %>%
  filter(!is.na(place))
```

```{r}
gen_pois_him = getModel("him", "Stan/gen_pois.stan", back = T)
```

```{r}
him_final = Gen_Pois_Quantities(gen_pois_him, him, back = T)
```

```{r}
output <- df_visual(him_final, him)
all_df <- output$all_df
result <- output$result
```

```{r}
p16 <- plotting(all_df, result, 'him')
print(p16)
```

### Hurdle

```{r}
hurdle1_him = getModel("him", "Stan/gen_pois_hurdle.stan", back = T)
```

```{r}
him_final_hurdle = Hurdle_Pois_Quantities(hurdle1_him, him, back = T, hurdle = 0)
```

```{r}
output <- df_visual(him_final_hurdle, him)
all_df <- output$all_df
result <- output$result
```

```{r}
p16_5 <- plotting(all_df, result, 'him')
print(p16_5)
```


## 14 here

### Gen

try hurdle, don't prioritize
```{r}
here <- sbc %>%
  filter(tolower(text) == 'here') %>%
  filter(!is.na(place))
```

```{r}
gen_pois_here = getModel("here", "Stan/gen_pois.stan", back = T)
```

```{r}
here_final = Gen_Pois_Quantities(gen_pois_here, here, back = T)
```

```{r}
output <- df_visual(here_final, here)
all_df <- output$all_df
result <- output$result
```

```{r}
p17 <- plotting(all_df, result)
print(p17)
```


### Hurdle

```{r}
hurdle1_here = getModel("here", "Stan/gen_pois_hurdle.stan", back = T)
```

```{r}
here_final_hurdle = Hurdle_Pois_Quantities(hurdle1_here, here, back = T, hurdle = 0)
```

```{r}
output <- df_visual(here_final_hurdle, here)
all_df <- output$all_df
result <- output$result
```

```{r}
p17_5 <- plotting(all_df, result, 'here')
print(p17_5)
```

## 15 if

### Gen

if we have time, try making the parameters of the place dependent on length 

```{r}
if_ <- sbc %>%
  filter(tolower(text) == 'if') %>%
  filter(!is.na(place))
```

```{r}
gen_pois_if = getModel("if", "Stan/gen_pois.stan", back = F)
```

```{r}
if_final = Gen_Pois_Quantities(gen_pois_here, if_, back = F)
```

```{r}
output <- df_visual(if_final, if_)
all_df <- output$all_df
result <- output$result
```

```{r}
p18 <- plotting(all_df, result)
print(p18)
```

## 16 man

### Gen

dont know how to fix, leave it

```{r}
man <- sbc %>%
  filter(tolower(text) == 'man') %>%
  filter(!is.na(place))
```

```{r}
gen_pois_man = getModel("man", "Stan/gen_pois.stan", back = T)
```

```{r}
man_final = Gen_Pois_Quantities(gen_pois_man, man, back = T)
```

```{r}
output <- df_visual(man_final, man)
all_df <- output$all_df
result <- output$result
```

```{r}
p19 <- plotting(all_df, result, 'man')
print(p19)
```

## 17 maybe

### Gen

```{r}
maybe <- sbc %>%
  filter(tolower(text) == 'maybe') %>%
  filter(!is.na(place))
```

```{r}
gen_pois_maybe = getModel("maybe", "Stan/gen_pois.stan", back = F)
```

```{r}
maybe_final = Gen_Pois_Quantities(gen_pois_maybe, maybe, back = F)
```

```{r}
output <- df_visual(maybe_final, maybe)
all_df <- output$all_df
result <- output$result
```

```{r}
p20 <- plotting(all_df, result, 'maybe')
print(p20)
```

## 18 so

### Gen

try bimodal

```{r}
so <- sbc %>%
  filter(tolower(text) == 'so') %>%
  filter(!is.na(place))
```

```{r}
gen_pois_so = getModel("so", "Stan/gen_pois.stan", back = F)
```

```{r}
so_final = Gen_Pois_Quantities(gen_pois_so, so, back = F)
```

```{r}
output <- df_visual(so_final, so)
all_df <- output$all_df
result <- output$result
```

```{r}
p21 <- plotting(all_df, result)
print(p21)
```

## 19 stuff

### Gen

similar to him, them, try hurdle
```{r}
stuff <- sbc %>%
  filter(tolower(text) == 'stuff') %>%
  filter(!is.na(place))
```

```{r}
cri <- check_back(stuff)
cri
```

```{r}
gen_pois_stuff = getModel("stuff", "Stan/gen_pois.stan", back = T)
```

```{r}
stuff_final = Gen_Pois_Quantities(gen_pois_stuff, stuff, back = T)
```

```{r}
output <- df_visual(stuff_final, stuff)
all_df <- output$all_df
result <- output$result
```

```{r}
p22 <- plotting(all_df, result, 'stuff')
print(p22)
```

### Hurdle

```{r}
hurdle1_stuff = getModel("stuff", "Stan/gen_pois_hurdle.stan", back = T)
```

```{r}
stuff_final_hurdle = Hurdle_Pois_Quantities(hurdle1_stuff, stuff, back = T, hurdle = 0)
```

```{r}
output <- df_visual(stuff_final_hurdle, stuff)
all_df <- output$all_df
result <- output$result
```

```{r}
p22_5 <- plotting(all_df, result, 'stuff')
print(p22_5)
```
## 20 be

skip for now

```{r}
be <- sbc %>%
  filter(tolower(text) == 'be') %>%
  filter(!is.na(place))
```

```{r}
gen_pois_be = getModel("be", "Stan/gen_pois.stan", back = T)
```
### Gen
```{r}
be_final = Gen_Pois_Quantities(gen_pois_be, be, back = T)
```

```{r}
output <- df_visual(be_final, be)
all_df <- output$all_df
result <- output$result
```

```{r}
p23 <- plotting(all_df, result, 'be')
print(p23)
```

## 21 can 

try hurdle

```{r}
can <- sbc %>%
  filter(tolower(text) == 'can') %>%
  filter(!is.na(place))
```


```{r}
gen_pois_can = getModel("can", "Stan/gen_pois.stan", back = F)
```

### Gen

```{r}
can_final = Gen_Pois_Quantities(gen_pois_can, can, back = F)
```

```{r}
output <- df_visual(can_final, can)
all_df <- output$all_df
result <- output$result
```

```{r}
p24 <- plotting(all_df, result, 'can')
print(p24)
```




More complicated ones

## 22 all

```{r}
all <- sbc %>%
  filter(tolower(text) == 'all') %>%
  filter(!is.na(place))
```

```{r}
gen_pois_all = getModel("all", "Stan/gen_pois.stan", back = T)
```

### Gen
```{r}
all_final = Gen_Pois_Quantities(gen_pois_can, all, back = T)
```


```{r}
output <- df_visual(all_final, all)
all_df <- output$all_df
result <- output$result
```

```{r}
p25 <- plotting(all_df, result, 'all')
print(p25)
```

## 23 before
```{r}
before <- sbc %>%
  filter(tolower(text) == 'before') %>%
  filter(!is.na(place))
```

```{r}
mix_before = getModel("before", "Stan/mixture_model.stan", back = F)
```

### Mix


```{r}
before_final_mix = Mix_Pois_Quantities(mix_before, before)
```

```{r}
output <- df_visual(before_final_mix, before)
all_df <- output$all_df
result <- output$result
```

```{r}
p26 <- plotting(all_df, result, 'before')
print(p26)
```
## 24 about

### Gen

```{r}
output <- generate_vis("about", "gen")
p27 <- output[[1]]
gen_about_model <- output[[2]]
gen_about_final <- output[[3]]
print(p27)
```




## 25 around
### Gen

```{r}
output <- generate_vis("around", "gen")
p28 <- output[[1]]
gen_around_model <- output[[2]]
gen_around_final <- output[[3]]
print(p28)
```
### hurdle0

```{r}
output <- generate_vis("around", "hur0")
p_around_hur0 <- output[[1]]
hur0_around_model <- output[[2]]
hur0_around_final <- output[[3]]
print(p_around_hur0)
```


## 26 be
### Gen

```{r}
output <- generate_vis("be", "gen")
p_be_gen <- output[[1]]
gen_be_model <- output[[2]]
gen_be_final <- output[[3]]
print(p_be_gen)
```


## 27 five
### Gen

```{r}
output <- generate_vis("five", "gen")
p_five_gen <- output[[1]]
gen_five_model <- output[[2]]
gen_five_final <- output[[3]]
print(p_five_gen)
```




